Sea: A lightweight data-placement library for Big Data scientific computing

### 2022-07-04 paper/sea-comp/paper.tex
notebook and text updates

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{longtable}
\usepackage[binary-units=true]{siunitx}
\usepackage{multirow}
\usepackage{subcaption}
%\usepackage{algorithm}
\usepackage[ruled,norelsize]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{xspace}

@@

    {\noindent} Where, \\
    $N$ is the network bandwidth \\
    $c$ is the number of compute nodes used \\
    $s$ is the number of Lustre storage nodes \\
    $p$ is the number of parallel application processes \\
    $d_{r}$ is the read bandwidth of a single Lustre storage disk \\
    $d_{w}$ is the write bandwidth of a single Lustre storage disk \\

@@

      We use the BigBrain~\cite{amunts2013bigbrain}, a one-of-a-kind histology
      dataset of the human brain, as a representative scientific dataset. For
      all our experiments, we utilize the \SI{20}{\micro\meter} dataset, which
      totals to approximately \SI{603}{\gibi\byte} \MD{Are you sure it's 603? I had calculated 606~GiB for my Spark \& Dask paper}. The dataset was broken down
      into 1000 files each consisting of \SI{617}{\mebi\byte} of data.
      %of data as well as 5000 blocks each \SI{124}{\mebi\byte} in size.

      We evaluated Sea using 4 different experimental conditions: 1) varying the
      number of nodes, 2) varying the number of disks, 3) varying the number of
      threads, and 4) varying the number of iterations. Experimental condition 1 \MD{Is the number of thread constant when varying nodes? i.e., 64 threads total for either 8 nodes or 4 nodes}
      tests the effects of increasing concurrent accesses to Lustre while fixing
      disk parallel threads. Condition 2 varies disk contention while fixing
      contention to Lustre, whereas 3 tests the effects of contention on both
      Lustre and local storage. Experimental condition 4 varies the total amount
      of intermediate data produced by the application. The fixed conditions for
      the experiment were 5 nodes, 6 processes, 6 disks, 10 iterations and 1000
      blocks. Sea in-memory (flushing and eviction of only the last iteration of
      files) strategy was used for all conditions.

@@

      Each file system was benchmarked using \texttt{dd} using 5 repetitions. \MD{What dd command was used? In particular, the block size and the total data size transfered}
      The average bandwidths are reported in Table~\ref{table:sea-comp:fs}

@@

    Sea cannot be used with operating systems that are not Linux-based, and
    therefore, the use of Sea limits application portability \MD{Does Sea really limits portability? The application could still be used on other platform easily. i.e., Sea is limited to Posix-based system but doesn't limit application by itself, since it no rewrite of the application is required.}. However, HPC
    systems commonly use Linux operating systems, thus, it is not limiting for
    its intended use case. Furthermore, we provide publicly available containers
    to simplify the usage of Sea on various other operating systems.

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{longtable}
\usepackage[binary-units=true]{siunitx}
\usepackage{multirow}
\usepackage{subcaption}
%\usepackage{algorithm}
\usepackage[ruled,norelsize]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{xspace}
\usepackage{footmisc}

@@

    {\noindent} Where, \\
    $N$ is the network bandwidth \\
    $c$ is the number of compute nodes used \\
    $s$ is the number of Lustre storage nodes \\
    $p$ is the number of parallel application processes \\
    $d$ is the number of Lustre storage disks \\
    $d_{r}$ is the read bandwidth of a single Lustre storage disk \\
    $d_{w}$ is the write bandwidth of a single Lustre storage disk \\

@@

      We use the BigBrain~\cite{amunts2013bigbrain}, a one-of-a-kind histology
      dataset of the human brain, as a representative scientific dataset. For
      all our experiments, we utilize the \SI{20}{\micro\meter} dataset, which
      totals to approximately \SI{603}{\gibi\byte}. The dataset was broken down
      into 1000 files each consisting of \SI{617}{\mebi\byte} of data.
      %of data as well as 5000 blocks each \SI{124}{\mebi\byte} in size.

      We evaluated Sea using 4 different experimental conditions: 1) varying the
      number of nodes, 2) varying the number of disks, 3) varying the number of
      threads, and 4) varying the number of iterations. Experimental condition 1
      tests the effects of increasing concurrent accesses to Lustre while fixing
      disk parallel threads (i.e., the number of threads per node is constant).
      Condition 2 varies disk contention while fixing
      contention to Lustre, whereas condition 3 evaluates the effects of contention on both
      Lustre and local storage. Experimental condition 4 varies the total amount
      of intermediate data produced by the application. The fixed conditions for
      the experiment were 5 nodes, 6 processes, 6 disks, 10 iterations and 1000
      blocks. Sea in-memory (flushing and eviction of only the last iteration of
      files) strategy was used for all conditions.

@@

      Each file system was benchmarked 5 times with the \texttt{dd} command \footnote{\url{https://github.com/big-data-lab-team/Sea/blob/master/benchmarks/scripts/bench_disks.sh}}.
      The average bandwidths are reported in Table~\ref{table:sea-comp:fs}

@@

    Sea cannot be used with operating systems that are not Linux-based, and
    therefore, the use of an application with Sea has limited portability. However, Linux-based operating systems
    are ubiquitous in HPC, and therefore, Sea is not limiting for
    its intended use case. Furthermore, we provide publicly available containers~\footnote{\url{https://github.com/orgs/big-data-lab-team/packages?repo_name=Sea}}
    to simplify the usage of Sea on various other operating systems.
